Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}

### 2022-11-12 nakayama/paper.tex
Minor edits, fitted text to 80 columns

\section{Introduction}

The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations.  Research in the field now centers around \emph{commutative rings}---rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$---and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them. 
Commutative algebra has deep connections with other areas of theoretical mathematics, including number theory and algebraic geometry.

Commutative algebra also has broad applications to science and technology.  For instance, it has been integral to advances in robotics \cite{cox-little-oshea}, and has helped form our current understanding of the human genome \cite{genetic-algebra}. 
The commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, has become a fundamental computational tool in 
coding theory and cryptography (e.g., see  \cite{grobner-bases-cryptography}).
A implementation of Buchberger's algorithm \cite{buchberger} for determining 
Gr\"obner bases of ideals in polynomial rings has been proved correct within the proof assistant Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an integrated formal development of the algorithm in Coq has also been carried out \cite{persson2001integrated} (see also \cite{grobner-type-theory}).

Our goal is to newly formalize theoretical, rather than computational, commutative algebra in Coq. 
We formally prove \emph{Nakayama's Lemma} \cite{nakayama-1951, azumaya}, an essential result in the field. 
In doing so, we formalize algebraic structures that are fundamental to higher-level algebra, such as 
\emph{local rings} and \emph{modules over commutative rings}, and \emph{quotient rings and modules}.  
Rather than build upon some of the basic objects from abstract algebra, such as groups and rings, that have been formalized in Coq, e.g., in the  
\emph{Mathematical Components Library} 
\cite{mathcomp}, we start from scratch. \todo{To do: Verify whether MathComp only formalized finite algebraic structures}
 The theory, including the formalization of all algebraic structures, makes up approximately $100$ kB and 3300 lines of code.

The notion of a module over a ring is an extension of the linear-algebraic notion of a vector space over a field, ubiquitous in mathematics and its applications. 
Less frequently referred to as the \emph{Krull-Azumaya theorem}\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra} \cite{matsumura}:  ``{This simple but important lemma is due to T.\ Nakayama, G.\ Azumaya
and W.\ Krull. Priority is obscure, and although it is usually called the Lemma of Nakayama, late Prof.\  Nakayama did not like the name.''}}\,\cite{nagata}, Nakayama's Lemma 
describes one way that a finitely generated module over an arbitrary commutative ring acts like a vector space over a field.  
True to the convention that ``lemma'' often refers to a result serving as a stepping stone toward another goal, Nakayama's Lemma is applied widely throughout the field, and the result is typically introduced in a first graduate course in commutative algebra \cite{atiyah-macdonald, matsumura, eisenbud}.

%It is widely applied throughout algebra. %, true to .  However, Nakayama's lemma 
%is also an important result in its own right, and can be thought of as one of the fundamental theorems of 
%commutative algebra, not unlike the fundamental theorems of calculus describing the inverse relationship between derivatives and integrals or the fundamental theorem of arithmetic that makes precise the notion of unique factorization. 
%, or the fundamental theorem of algebra (or \emph{d'Alembert's theorem}) on the roots of complex polynomials.

\section{Mathematical Basis and Motivation}

\subsection{The Fundamental Algebraic Structures}

Here, we give a brief description of the major mathematical structures from commutative algebra that are relevant to Nakayama's Lemma.

@@

A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal with respect to inclusion, i.e., no other proper ideal strictly contains it. 
Returning to our example of the ring of integers, $6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, 
so $6 \mathbb{Z}$ is not a maximal ideal of $\mathbb{Z}$. 
However, no proper ideal $I$ contains $2 \mathbb{Z}$:  If $2 \mathbb{Z}\subsetneq I \subsetneq \mathbb{Z}$, then $I$  would necessarily contain an odd number $n$.  Writing $n=2k+1$ for some integer $k$, we notice that since $-2k$ is in $2\mathbb{Z}$, it is also an element of the larger set $I$, and since $I$ is an abelian group under addition, $(2k+1) + (-2k) = 1$ is also in the ideal $I$. 
However, in this case, every integer $n = n \cdot 1$ is in $I$ by absorption, so $I = \mathbb{Z}$ is not a proper ideal, a contradiction.

@@

\paragraph{Local rings.}
A commutative ring is \emph{local} if it has exactly one maximal ideal.  
Every field is local since the only proper ideal of a field is the zero ideal, though by our observations above, the ring of integers is not local. 
However, the set of all rational numbers that can be written with an odd denominator does form a subring of all rational numbers, and its unique maximal ideal consists of the elements with even numerator; in fact, this ring is the so-called \emph{localization} of $\mathbb{Z}$ at the maximal ideal $2 \mathbb{Z}$.  
The ring of integers modulo $n>1$ is local if and only if $n$ is a power of a prime number $p$,  in which case the unique maximal ideal consists of all multiples of $p$.

@@

%Hence the ring of integers is not local, but 
%the ring of integers modulo an integer $n>1$,  often denoted $\mathbb{Z}/n\mathbb{Z}$ or $\mathbb{Z}_n$, are local

@@

From this definition, one can see that a module over a field $F$ is precisely an $F$-vector space, so the notion of a module over an arbitrary commutative ring extends that of a vector space over a field. 
Finitely generated vector spaces form the foundation for matrix algebra, and the extension of this notion to module theory is needed to state Nakayama's Lemma.  We call an $R$-module $M$ \emph{finitely generated} if there exist a fixed finite number of elements $u_1, \ldots, u_n$ of $M$ with the following property:  Given any  $w \in M$, there exist $r_1, \ldots, r_n \in R$ for which  
\[
w = r_1 u_1 + r_1 u_2 + \cdots + r_n u_n.
\]
The set $\{u_1, \ldots, u_n\}$ is called a \emph{generating set} for the $M$ as an $R$-module.

When $R=F$ is a field and $M=V$ is a finite-dimensional vector space over $F$, one can choose $u_1, \ldots, u_n$ to be a basis for $V$, i.e., $n = \dim V$.  In this case, the choice of scalar coefficients in the expression above for $w \in V$ is unique.  When $R$ is not a field, however, such an expression is typically not unique.

@@

In order to state Nakayama's Lemma, we first explain some notation:  If $I$ is an ideal of a commutative ring $R$ and 
 $M$ is an $R$-module, then $IM$ is the set of elements of the form 
	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where, for some positive integer $k$, $a_1, \ldots, a_k \in I$ and $u_1, \ldots, u_k \in M$.  
Notice that due to the absorption property of ideals, $IM$ is an $R$-module contained in $M$.

If an $R$-module $M$ consists of only one element, this element must be its additive identity $0$ as an abelian group under addition.  The notation $M=0$ means that we are in this situtation.

@@

We point out that there are alternate statements of Nakayama's Lemma that do not require the hypothesis that $R$ must be local.  One can replace the unique maximal ideal with the Jacobson radical of the ring, which is the intersection of all maximal ideals. Alternatively, $I$ is an arbitrary proper ideal of a commutative ring $R$ and  
 $M$ is a finitely generated $R$-module for which $M=I M$, then this ensures the existence of a ring element $r$ congruent to $1$ modulo $I$ such that $rM = 0$, i.e., $r u = 0$ for every $u \in M$.

\section{Formalization}

We start by describing our process of formalizing the required algebraic structures detailed in the previous section.  Then, with that in hand, we move on to the formal proof of Nakayama's Lemma.

\subsection{Our Algebraic Hierarchy}

\begin{figure}[t]
\caption{The hierarchy of our algebraic structures}
\includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
\centering
\todo[inline]{To do:  Double check source code to verify whether the hierarchy figure should be altered (subobjects, quotients, finitely generated modules, local rings, etc.)}
\end{figure}

@@

\begin{minted}{coq}
  Infix "==" := equiv (at level 60, no associativity).
  Class Semigroup := {
    semigroup_assoc:
      forall (a b c: Carrier),
        a <o> b <o> c == a <o> (b <o> c);
  }.
  Class Monoid := {
    monoid_semigroup :> Semigroup equiv op;
    monoid_ident_l:
      forall (a: Carrier), ident <o> a == a;
    monoid_ident_r:
      forall (a: Carrier), a <o> ident == a;
  }.
  Class Group := {
    group_monoid :> Monoid equiv op ident;
    group_inv_l:
      forall (a: Carrier), inv a <o> a == ident;
    group_inv_r:
      forall (a: Carrier), a <o> inv a == ident;
  }.
\end{minted}
The lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
the monoid typeclass into a semigroup.

@@

An algebraic quotient is, roughly, the set of equivalence classes of an algebraic structure with respect to an equivalence relation on its elements, for which the set of equivalence classes inherit the same kind of algebraic structure. 
For example, consider the quotient of a group modulo a subgroup, i.e. a subset of elements of the group that it itself a group under the group operations. 
Under equivalence relation on the group, every element of the subgroup must be in the same equivalence class as the identity.  
With \texttt{P} the predicate for the subgroup, there are two ways to
make an equivalence relation from this description.

@@

\emily[inline]{It would be nice to differentiate between our structures that are typeclasses (e.g., {\ttfamily Ideal}), and other definitions (e.g., {\ttfamily maximal ideal})}
Next, we formally defined a maximal ideal, a proper ideal that are maximal with respect to inclusion, i.e., if it is strictly contained in another ideal, this larger ideal must be the entire ring. 
Below is the definition in Coq,
which uses \texttt{P} as the predicate for the ideal.

@@

\emily[inline]{Emily:  Unfortunately, I think we need to update naming conventions since in mathematics, ``vector'' is reserved for an element of a vector space over a field, rather than an element of an arbitrary module.  So this could cause confusion.  Similar with ``basis,'' which is especially tricking since two different generating sets of a finitely generated module can have different sizes, but all bases of a vector space have the same cardinality, and an element of a module can typically be written as a scalar combination in multiple ways, while bases are linearly independent.  I've proposed a rewrite of the blue paragraph right above it.  Drew, can you double check it for accuracy with respect to the code? 
}
\emily[inline]{
We'll also need to update the code.  I think {\ttfamily vectors} should be something like {\ttfamily scalar-combinations}, and {\ttfamily basis} something like {\ttfamily generating-set}. 
}

@@

\textcolor{blue}{Here we needed to formalize the notion of linear combinations of
coefficients and module vectors. This was done by dependently typed vectors,
i.e. lists parameterized by their length. Because there is an overload of the
term ``vector'', we will use that term to refer to module vectors, and use the
term ``list'' to mean length-parameterized lists. As we don't use the simpler
kind of lists, this avoids any name collisions. A finitely generated module is
like the vector space \(\mathbf{R}^{n}\) in that there are finitely many
vectors which can generate all other vectors, for \(\mathbf{R}^{n}\) one such
collection of generators are \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \textellipsis, \(\mathbf{e}_{n} =
  \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\). In our code,
\texttt{M} is the type of module elements, \texttt{R} is the type of ring
elements which act as coefficients, and \texttt{t A n} is a list whose elements
are of type \texttt{A} and whose length is \texttt{n}.
}

@@

\subsection{Building the Formal Proof}

Beyond formalizing the relevant structures from higher algebra, we also formally establish some basic theory. 
For instance, a \emph{unit} of a commutative ring $R$ is an element $x \in R$ with a multiplicative inverse, i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the multiplicative identity $1 \in R$.

@@

    If \(I_{1}\) is not a maximal ideal,
    then there exists a strictly larger proper ideal \(I_{2}\) of $R$, i.e.
    $x\in I_{1}\subsetneq I_{2} \subsetneq R$.
    Moreover, if  \(I_{2}\) is not maximal, then there
    exists a strictly larger proper ideal $I_{3} \supsetneq I_2$.

@@

    It is straightfoward to show that \(\bigcup_{k=1}^{\infty} I_{k}\) satisfies the definition of an ideal of $R$, 
    and this union certainly contains \(x\). So by Zorn's lemma, since every ascending chain of ideals containing $x$ 
    with respect to inclusion has its union as an upper bound, there exists a maximal
    ideal of \(R\) containing \(x\).
\end{quote}

@@

We needed a lemma before moving on to prove the main theorem which states that
for a finitely generated $R$-module \(M\) with generating set\emily{Changed ``basis'' to ``generating set'' here}
\(b_{1}, b_{2}, \dots, b_{n}\), any element \(x\in I M\), where \(I\) is an
ideal of $R$, can be written as a linear combination of the basis vectors with
coefficients coming from \(I\). \emily{I'm confused:  Isn't this how we defined $IM$? Where are the $u$'s and $a$'s coming from?}
 The proof of this lemma is straightforward and
follows the standard, informal mathematical argument, which inductively goes
through the vectors needed to generate \(x\) and shows that each vector can be
rewritten in terms of the basis vectors times elements of the ideal \(I\) as
follows.
\begin{align*}
  x & = \sum_{k=1}^{m} u_{k} a_{k} \\
    & = \sum_{k=1}^{m} u_{k} (r_{k1} b_{1} + \cdots + r_{kn} b_{n}) \\
    & = \sum_{j=1}^{n} (u_{1} r_{1j} + \cdots + u_{m} r_{mj}) b_{j}
\end{align*}
Since each \(u_{k}\) comes from the ideal \(I\), the absorbing property of
ideals guarantees that \(u_{k} r_{k j}\) is also contained in \(I\). As ideals
are also closed under addition, it follows that \(u_{1} r_{1j} + \cdots +
u_{m} r_{m j}\) are all elements of \(I\). Thus, \(x\) can be written as a
linear combination of the basis vectors with the coefficients coming from
\(I\).

@@

Now we move to describe the skeleton of our formal proof of Nakayama's lemma. 
We proceed by induction on the number of elements in a generating set for the finitely-generated module $M$. 
. The base case where \(M\) is generated by 0 vectors is by
definition true since an empty linear combination is conventionally taken to be
the zero vector. \emily{I think we should consider using one generator for the base case. }
The inductive case where \(M\) is generated by the vectors
\(b_{1}, \dots, b_{m}, b_{m+1}\). By assumption \(M = \mathfrak{m} M\) with
\(b_{1}\in M\). Then \(b_{1}\in\mathfrak{m} M\) meaning that by our lemma,
there exists a linear combination for \(b_{1}\), say
\[b_{1} = u_{1} b_{1} + \cdots + u_{m+1} b_{m+1}\]
for some \(u_{1}, \dots, u_{m+1}\in\mathfrak{m}\). Collect the \(b_{1}\) terms
on the left-hand side of the equation to get that
\[(1 - u_{1}) b_{1} = u_{2} b_{2} + \cdots + u_{m+1} b_{m+1}\text{.}\]
As mentioned when defining maximal ideals, \(\mathfrak{m}\) can only contain
non-units. Namely, \(u_{1}\) must be a non-unit. Then we had already proven
that \(1 - u_{1}\) is a unit as we are in a local ring. Let \(v_{1}\) be the
multiplicative inverse of \(1 - u_{1}\), and multiply it on both sides of the
equation.
\begin{align*}
  v_{1} (1 - u_{1}) b_{1}
    & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
  1 b_{1} & = \\
  b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
\end{align*}
We have thus found that one of the basis vectors is not needed to generate this
module. Using the induction hypothesis, we have that \(M = 0\). Showing that
the induction hypothesis holds in Coq takes more work than in an informal
proof, but this extra work is just a lot of bookkeeping.

>>>>

\section{Introduction}
The mathematical field of \emph{commutative algebra} stems from the study of
solutions to polynomial equations. Research in the field now centers around
\emph{commutative rings}---rings in which order does not affect multiplication,
i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$---and
fundamental algebraic objects associated to them:  \emph{ideals} of these
rings, and \emph{modules} over them. Commutative algebra has deep connections
with other areas of theoretical mathematics, including number theory and
algebraic geometry.

Commutative algebra also has broad applications to science and technology. For
instance, it has been integral to advances in robotics \cite{cox-little-oshea},
and has helped form our current understanding of the human genome
\cite{genetic-algebra}. The commutative-algebraic notion of a Gr\"{o}bner
basis, a special type of generating set for an ideal in a ring of polynomials,
has become a fundamental computational tool in coding theory and cryptography
(e.g., see  \cite{grobner-bases-cryptography}). A implementation of
Buchberger's algorithm \cite{buchberger} for determining Gr\"obner bases of
ideals in polynomial rings has been proved correct within the proof assistant
Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an
integrated formal development of the algorithm in Coq has also been carried out
\cite{persson2001integrated} (see also \cite{grobner-type-theory}).

Our goal is to newly formalize theoretical, rather than computational,
commutative algebra in Coq. We formally prove \emph{Nakayama's Lemma}
\cite{nakayama-1951, azumaya}, an essential result in the field. In doing so,
we formalize algebraic structures that are fundamental to higher-level algebra,
such as \emph{local rings} and \emph{modules over commutative rings}, and
\emph{quotient rings and modules}. Rather than build upon some of the basic
objects from abstract algebra, such as groups and rings, that have been
formalized in Coq, e.g., in the \emph{Mathematical Components Library}
\cite{mathcomp}, we start from scratch.
\todo{To do: Verify whether MathComp only formalized finite algebraic
  structures. Drew is about as certain as he can be that this is the case.}
The theory, including the formalization of all algebraic structures, makes up
approximately $100$ kB and 3300 lines of code.

The notion of a module over a ring is an extension of the linear-algebraic
notion of a vector space over a field, ubiquitous in mathematics and its
applications. Less frequently referred to as the \emph{Krull-Azumaya theorem}
\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra}
  \cite{matsumura}: ``{This simple but important lemma is due to T.\ Nakayama,
  G.\ Azumaya, and W.\ Krull. Priority is obscure, and although it is usually
  called the Lemma of Nakayama, late Prof.\  Nakayama did not like the
  name.''}}
\,\cite{nagata}, Nakayama's Lemma describes one way that a finitely generated
module over an arbitrary commutative ring acts like a vector space over a
field. True to the convention that ``lemma'' often refers to a result serving
as a stepping stone toward another goal, Nakayama's Lemma is applied widely
throughout the field, and the result is typically introduced in a first
graduate course in commutative algebra \cite{atiyah-macdonald, matsumura,
eisenbud}.

% It is widely applied throughout algebra. %, true to. However, Nakayama's lemma 
% is also an important result in its own right, and can be thought of as one of
% the fundamental theorems of 
% commutative algebra, not unlike the fundamental theorems of calculus
% describing the inverse relationship between derivatives and integrals or the
% fundamental theorem of arithmetic that makes precise the notion of unique
% factorization.
% , or the fundamental theorem of algebra (or \emph{d'Alembert's theorem}) on
% the roots of complex polynomials.

\section{Mathematical Basis and Motivation}
\subsection{The Fundamental Algebraic Structures}
Here, we give a brief description of the major mathematical structures from
commutative algebra that are relevant to Nakayama's Lemma.

@@

A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal
with respect to inclusion, i.e., no other proper ideal strictly contains it. 
Returning to our example of the ring of integers,
$6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, so
$6 \mathbb{Z}$ is not a maximal ideal of $\mathbb{Z}$. However, no proper ideal
$I$ contains $2 \mathbb{Z}$: If $2\mathbb{Z}\subsetneq I\subsetneq \mathbb{Z}$,
then $I$  would necessarily contain an odd number $n$. Writing $n=2k+1$ for
some integer $k$, we notice that since $-2k$ is in $2\mathbb{Z}$, it is also an
element of the larger set $I$, and since $I$ is an abelian group under
addition, $(2k+1) + (-2k) = 1$ is also in the ideal $I$. However, in this case,
every integer $n = n \cdot 1$ is in $I$ by absorption, so $I = \mathbb{Z}$ is
not a proper ideal, a contradiction.

@@

\paragraph{Local rings.}
A commutative ring is \emph{local} if it has exactly one maximal ideal. 
Every field is local since the only proper ideal of a field is the zero ideal,
though by our observations above, the ring of integers is not local. 
However, the set of all rational numbers that can be written with an odd
denominator does form a subring of all rational numbers, and its unique maximal
ideal consists of the elements with even numerator; in fact, this ring is the
so-called \emph{localization} of $\mathbb{Z}$ at the maximal ideal
$2\mathbb{Z}$. The ring of integers modulo $n>1$ is local if and only if $n$ is
a power of a prime number $p$, in which case the unique maximal ideal consists
of all multiples of $p$.

@@

% Hence the ring of integers is not local, but the ring of integers modulo an
% integer $n>1$, often denoted $\mathbb{Z}/n\mathbb{Z}$ or $\mathbb{Z}_n$, are
% local

@@

From this definition, one can see that a module over a field $F$ is precisely
an $F$-vector space, so the notion of a module over an arbitrary commutative
ring extends that of a vector space over a field. Finitely generated vector
spaces form the foundation for matrix algebra, and the extension of this notion
to module theory is needed to state Nakayama's Lemma. We call an $R$-module
$M$ \emph{finitely generated} if there exist a fixed finite number of elements
$u_1, \ldots, u_n$ of $M$ with the following property:  Given any  $w \in M$,
there exist $r_1, \ldots, r_n \in R$ for which  
\[w = r_1 u_1 + r_1 u_2 + \cdots + r_n u_n\text{.}\]
The set $\{u_1, \ldots, u_n\}$ is called a \emph{generating set} for the $M$ as
an $R$-module.

When $R = F$ is a field and $M = V$ is a finite-dimensional vector space over
$F$, one can choose $u_1, \ldots, u_n$ to be a basis for $V$, i.e.,
$n = \dim V$. In this case, the choice of scalar coefficients in the expression
above for $w \in V$ is unique. When $R$ is not a field, however, such an
expression is typically not unique.

@@

In order to state Nakayama's Lemma, we first explain some notation:  If $I$ is
an ideal of a commutative ring $R$ and $M$ is an $R$-module, then $IM$ is the
set of elements of the form $a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where, for
some positive integer $k$, $a_1, \ldots, a_k \in I$ and
$u_1, \ldots, u_k \in M$. Notice that due to the absorption property of ideals,
$I M$ is an $R$-module contained in $M$.

If an $R$-module $M$ consists of only one element, this element must be its
additive identity $0$ as an abelian group under addition. The notation $M=0$
means that we are in this situation.

@@

We point out that there are alternate statements of Nakayama's Lemma that do
not require the hypothesis that $R$ must be local. One can replace the unique
maximal ideal with the Jacobson radical of the ring, which is the intersection
of all maximal ideals. Alternatively, $I$ is an arbitrary proper ideal of a
commutative ring $R$ and $M$ is a finitely generated $R$-module for which
$M=I M$, then this ensures the existence of a ring element $r$ congruent to
$1$ modulo $I$ such that $r M = 0$, i.e., $r u = 0$ for every $u \in M$.

\section{Formalization}
We start by describing our process of formalizing the required algebraic
structures detailed in the previous section. Then, with that in hand, we move
on to the formal proof of Nakayama's Lemma.

\subsection{Our Algebraic Hierarchy}
\begin{figure}[t]
  \caption{The hierarchy of our algebraic structures}
  \includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
  \centering
\end{figure}
\todo[inline]{To do:  Double check source code to verify whether the hierarchy
figure should be altered (subobjects, quotients, finitely generated modules,
local rings, etc.) It looks good to Drew.}

@@

\begin{minted}{coq}
  Infix "==" := equiv (at level 60, no associativity).
  Class Semigroup := {
    semigroup_assoc:
      forall (a b c: Carrier),
        a <o> b <o> c == a <o> (b <o> c);
  }.
  Class Monoid := {
    monoid_semigroup :> Semigroup equiv op;
    monoid_ident_l:
      forall (a: Carrier), ident <o> a == a;
    monoid_ident_r:
      forall (a: Carrier), a <o> ident == a;
  }.
  Class Group := {
    group_monoid :> Monoid equiv op ident;
    group_inv_l:
      forall (a: Carrier), inv a <o> a == ident;
    group_inv_r:
      forall (a: Carrier), a <o> inv a == ident;
  }.
\end{minted}
Lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
the monoid typeclass into a semigroup.

@@

An algebraic quotient is, roughly, the set of equivalence classes of an
algebraic structure with respect to an equivalence relation on its elements,
for which the set of equivalence classes inherit the same kind of algebraic
structure. For example, consider the quotient of a group modulo a subgroup,
i.e., a subset of elements of the group that it itself a group under the group
operations. Under equivalence relation on the group, every element of the
subgroup must be in the same equivalence class as the identity. With \texttt{P}
the predicate for the subgroup, there are two ways to make an equivalence
relation from this description.

@@

\emily[inline]{It would be nice to differentiate between our structures that
  are typeclasses (e.g., {\ttfamily Ideal}), and other definitions (e.g.,
  {\ttfamily maximal ideal})}

Next, we formally defined a maximal ideal, a proper ideal that are maximal with
respect to inclusion, i.e., if it is strictly contained in another ideal, this
larger ideal must be the entire ring. Below is the definition in Coq, which
uses \texttt{P} as the predicate for the ideal.

@@

\emily[inline]{Emily:  Unfortunately, I think we need to update naming
  conventions since in mathematics, ``vector'' is reserved for an element of a
  vector space over a field, rather than an element of an arbitrary module.  So
  this could cause confusion.  Similar with ``basis,'' which is especially
  tricking since two different generating sets of a finitely generated module
  can have different sizes, but all bases of a vector space have the same
  cardinality, and an element of a module can typically be written as a scalar
  combination in multiple ways, while bases are linearly independent.  I've
  proposed a rewrite of the blue paragraph right above it.  Drew, can you
  double check it for accuracy with respect to the code? 
}
\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
  should be something like {\ttfamily scalar-combinations}, and
  {\ttfamily basis} something like {\ttfamily generating-set}. 
}

@@

\textcolor{blue}{Here we needed to formalize the notion of linear combinations
  of coefficients and module vectors. This was done by dependently typed
  vectors, i.e., lists parameterized by their length. Because there is an
  overload of the term ``vector'', we will use that term to refer to module
  vectors, and use the term ``list'' to mean length-parameterized lists. As we
  don't use the simpler kind of lists, this avoids any name collisions. A
  finitely generated module is like the vector space \(\mathbf{R}^{n}\) in that
  there are finitely many vectors which can generate all other vectors, for
  \(\mathbf{R}^{n}\) one such collection of generators are
  \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 & \cdots & 0\end{pmatrix}^{T}\),
  \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 & \cdots & 0\end{pmatrix}^{T}\),
  \textellipsis,
  \(\mathbf{e}_{n} = \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\).
  In our code, \texttt{M} is the type of module elements, \texttt{R} is the
  type of ring elements which act as coefficients, and \texttt{t A n} is a list
  whose elements are of type \texttt{A} and whose length is \texttt{n}.
}

@@

\subsection{Building the Formal Proof}
Beyond formalizing the relevant structures from higher algebra, we also
formally establish some basic theory. For instance, a \emph{unit} of a
commutative ring $R$ is an element $x \in R$ with a multiplicative inverse,
i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the
multiplicative identity $1 \in R$.

@@

    If \(I_{1}\) is not a maximal ideal, then there exists a strictly larger
    proper ideal \(I_{2}\) of $R$, i.e.,
    $x\in I_{1}\subsetneq I_{2} \subsetneq R$. Moreover, if  \(I_{2}\) is not
    maximal, then there exists a strictly larger proper ideal
    $I_{3} \supsetneq I_2$.

@@

    It is straight-forward to show that \(\bigcup_{k=1}^{\infty} I_{k}\)
    satisfies the definition of an ideal of $R$, and this union certainly
    contains \(x\). So by Zorn's lemma, since every ascending chain of ideals
    containing $x$ with respect to inclusion has its union as an upper bound,
    there exists a maximal ideal of \(R\) containing \(x\).
\end{quote}

@@

We needed a lemma before moving on to prove the main theorem which states that
for a finitely generated $R$-module \(M\) with generating set
\(b_{1}, b_{2}, \dots, b_{n}\), any element \(x\in I M\), where \(I\) is an
ideal of $R$, can be written as a linear combination of the generating set with
coefficients coming from \(I\).
\emily{I'm confused:  Isn't this how we defined $I M$? Where are the $u$'s and
  $a$'s coming from?}
In other words, given \(x\in I M\), there is by definition a linear combination
between elements \(u_{1}, \dots, u_{m}\in I\), and elements
\(a_{1},\dots, a_{m}\in M\), we need a lemma that states \(x\) can be written
as a linear combination between elements of \(I\) and the generating set
\(b_{1},\dots, b_{n}\in M\). This follows the informal mathematical argument
going inductively through the elements needed to generate \(x\) and shows that
each vector can be rewritten in terms of the generating set times coefficients
from the ideal \(I\) as follows.
\begin{align*}
  x & = \sum_{k=1}^{m} u_{k} a_{k} \\
    & = \sum_{k=1}^{m} u_{k} (r_{k1} b_{1} + \cdots + r_{kn} b_{n}) \\
    & = \sum_{j=1}^{n} (u_{1} r_{1j} + \cdots + u_{m} r_{mj}) b_{j}
\end{align*}
Since each \(u_{k}\) comes from the ideal \(I\), the absorbing property of
ideals guarantees that \(u_{k} r_{k j}\) is also contained in \(I\). As ideals
are also closed under addition, it follows that \(u_{1} r_{1j} + \cdots +
u_{m} r_{m j}\) are all elements of \(I\). Thus, \(x\) can be written as a
linear combination of the generating set with the coefficients coming from
\(I\).

@@

Now we move to describe the skeleton of our formal proof of Nakayama's lemma.
We proceed by induction on the number of elements in a generating set for the
finitely-generated module $M$. The base case where \(M\) is generated by 0
elements is by definition true since an empty linear combination is
conventionally taken to be the zero vector.
\emily{I think we should consider using one generator for the base case.}
The inductive case where \(M\) is generated by the vectors
\(b_{1}, \dots, b_{m}, b_{m+1}\). By assumption \(M = \mathfrak{m} M\).
With \(b_{1}\in M\), then \(b_{1}\in\mathfrak{m} M\) meaning that by our lemma,
there exists a linear combination for \(b_{1}\), say
\[b_{1} = u_{1} b_{1} + \cdots + u_{m+1} b_{m+1}\]
for some \(u_{1}, \dots, u_{m+1}\in\mathfrak{m}\). Collect the \(b_{1}\) terms
on the left-hand side of the equation to get that
\[(1 - u_{1}) b_{1} = u_{2} b_{2} + \cdots + u_{m+1} b_{m+1}\text{.}\]
As mentioned when defining maximal ideals, \(\mathfrak{m}\) can only contain
non-units. Namely, \(u_{1}\) must be a non-unit. Then we had already proven
that \(1 - u_{1}\) is a unit as we are in a local ring. Let \(v_{1}\) be the
multiplicative inverse of \(1 - u_{1}\), and multiply it on both sides of the
equation.
\begin{align*}
  v_{1} (1 - u_{1}) b_{1}
    & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
  1 b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
  b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
\end{align*}
We have thus found that one of the basis vectors is not needed to generate this
module. Using the induction hypothesis, we have that \(M = 0\). Showing that
the induction hypothesis holds in Coq takes more work than in an informal
proof, but this extra work is just a lot of bookkeeping.
